Assessing the impacts of time to detection distribution assumptions on detection probability estimation

### 2017-04-06 Supplement.tex
Updates to manuscript.

\documentclass[useAMS,usenatbib,referee,12pt]{article}
\usepackage[margin=1.0in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{parskip}
\usepackage[round]{natbib}
\usepackage{caption}
\usepackage{tabularx, booktabs}
\usepackage{float, placeins}
\usepackage{adjustbox}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{listings}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{rotating}

@@

\section{Tables}
\begin{table}[!ht]
\centering
\begin{tabular}{lll|ccc}
  \hline
Family & Mixture & Peaked & $\gamma$ & $\varphi$ & $\alpha$ \\ 
  \hline
Exponential & Non-mixture & &  & -1.827 &  \\ 
  & Mixture & & 0.65 & -2.138 &  \\ 
  \hline
  Gamma & Non-mixture & Non-peaked &  & -3.279 & 0.257 \\ 
  & & Peaked &  & -0.746 & 3.371 \\ 
  & Mixture & Non-peaked & 0.65 & -2.773 & 0.577 \\ 
  & & Peaked & 0.65 & -1.210 & 2.491 \\ 
  \hline
  Lognormal & Non-mixture & Non-peaked &  & -0.341 & 2.330 \\ 
  & & Peaked &  & -1.872 & 0.512 \\ 
  & Mixture & Non-peaked & 0.65 & -1.462 & 1.674 \\ 
  & & Peaked & 0.65 & -1.992 & 0.618 \\ 
  \hline
  Weibull & Non-mixture & Non-peaked &  & -1.165 & 0.418 \\ 
  & & Peaked &  & -2.042 & 1.829 \\ 
  & Mixture & Non-peaked & 0.65 & -2.063 & 0.687 \\ 
  & & Peaked & 0.65 & -2.201 & 1.621 \\ 
   \hline
\end{tabular}
\caption{\label{simvals}Table of parameter values used to generate data for: (i) the mixture vs. non-mixture simulation, and (ii) the constant vs. non-constant rate simulation.  Here $\gamma$ is a mixing parameter for the proportion of `hard to detect' individuals, $\varphi$ is the detection rate parameter, and $\alpha$ is the shape parameter.}
\end{table}

@@

Gamma & Non-mixture & Non-peaked &0.129&-0.001&0.098&-1.039&0.048&-0.104&-0.12&0.141&0.129 \\

@@

& Mixture & Non-peaked &0.128&-0.005&0.079&-1.051&-0.048&-0.126&-0.042&0.21&0.2 \\

@@

Lognormal & Non-mixture & Non-peaked &0.126&0.031&0.096&-1.047&0.163&-0.099&-0.071&0.31&0.079 \\

@@

& Mixture & Non-peaked &0.126&0.017&0.07&-1.068&0.006&-0.14&-0.038&0.341&0.191 \\

@@

Weibull & Non-mixture & Non-peaked &0.129&0.011&0.102&-1.04&0.101&-0.104&-0.127&0.204&0.086 \\

@@

& Mixture & Non-peaked &0.129&-0.002&0.081&-1.049&-0.028&-0.122&-0.069&0.204&0.183 \\

@@

Gamma & Non-mixture & Non-peaked &1.383&-3.941&0.121&0.072&0.39& & 0.316 \\

@@

& Mixture & Non-peaked &1.215&-2.7&0.121&0.079&0.332&0.79& 0.597 \\

@@

Lognormal & Non-mixture & Non-peaked &1.613&-2.444&0.151&0.077&0.353& & 3.287 \\

@@

& Mixture & Non-peaked &1.282&-2.051&0.14&0.079&0.312&0.706& 1.467 \\

@@

Weibull & Non-mixture & Non-peaked &1.57&-3.137&0.131&0.074&0.383& & 0.387 \\

@@

& Mixture & Non-peaked &1.294&-2.354&0.122&0.078&0.344&0.814& 0.653 \\

@@

\caption{\label{tbl:sim3}Table of parameter values used to generate data for simulations with covariates.  Here, $\gamma$ is a mixing parameter for the proportion of `hard to detect' individuals, $\beta$'s are fixed effects, $\sigma$'s are random effect standard deviations, $\alpha$ is a shape parameter, and superscripts of $A$ and $D$ indicate abundance and detection parameters, respectively.}

@@

%  Gamma & Non-mixture & Non-peaked & 1.383 & 0.129 & -0.001 & 0.098 & -1.039 & -3.941 & 0.048 & -0.104 & -0.120 & 0.141 & 0.129 & 0.121 & 0.072 & 0.390 &  & 0.316 \\ 

@@

%   & Mixture & Non-peaked & 1.215 & 0.128 & -0.005 & 0.079 & -1.051 & -2.700 & -0.048 & -0.126 & -0.042 & 0.210 & 0.200 & 0.121 & 0.079 & 0.332 & 0.790 & 0.597 \\ 

@@

%  Lognormal & Non-mixture & Non-peaked & 1.613 & 0.126 & 0.031 & 0.096 & -1.047 & -2.444 & 0.163 & -0.099 & -0.071 & 0.310 & 0.079 & 0.151 & 0.077 & 0.353 &  & 3.287 \\ 

@@

%   & Mixture & Non-peaked & 1.282 & 0.126 & 0.017 & 0.070 & -1.068 & -2.051 & 0.006 & -0.140 & -0.038 & 0.341 & 0.191 & 0.140 & 0.079 & 0.312 & 0.706 & 1.467 \\ 

@@

%  Weibull & Non-mixture & Non-peaked & 1.570 & 0.129 & 0.011 & 0.102 & -1.040 & -3.137 & 0.101 & -0.104 & -0.127 & 0.204 & 0.086 & 0.131 & 0.074 & 0.383 &  & 0.387 \\ 

@@

%   & Mixture & Non-peaked & 1.294 & 0.129 & -0.002 & 0.081 & -1.049 & -2.354 & -0.028 & -0.122 & -0.069 & 0.204 & 0.183 & 0.122 & 0.078 & 0.344 & 0.814 & 0.653 \\ 

@@

\begin{table}[ht]
\footnotesize\centering
\begin{tabular}{l|l|l|l|cccc|cccc}
 \multicolumn{4}{c|}{ } & \multicolumn{4}{c|}{\underline{Non-mixture model}} & \multicolumn{4}{c}{\underline{Mixture model}} \\
 \multicolumn{4}{c|}{ } & Med $p$ & Q($p$) & 50\% & 90\% & Med $p$ & Q($p$) & 50\% & 90\% \\ 
  \hline
  \hline
 \parbox[t]{2mm}{\multirow{14}{*}{\rotatebox[origin=c]{90}{TTDD used to simulate data}}} & \parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Non-mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}} & Gamma & 0.67 & 0.84 & 0.11 & 0.94 & 0.76 & 0.92 & 0.00 & 0.70 \\ 
   &  &  & Lognormal & 0.54 & 0.60 & 0.81 & 1.00 & 0.68 & 0.88 & 0.05 & 0.79 \\ 
   &  &  & Weibull & 0.55 & 0.61 & 0.79 & 0.99 & 0.69 & 0.84 & 0.16 & 0.87 \\ 
  \cline{3-12}
 & & &  Exponential & 0.49 & 0.45 & 0.51 & 0.93 & 0.45 & 0.30 & 0.47 & 0.86 \\ 
  \cline{3-12}
 & & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} & Gamma & 0.48 & 0.46 & 0.57 & 0.90 & 0.57 & 0.72 & 0.42 & 0.85 \\ 
   &  &  & Lognormal & 0.49 & 0.45 & 0.53 & 0.93 & 0.54 & 0.69 & 0.37 & 0.89 \\ 
   &  &  & Weibull & 0.48 & 0.48 & 0.40 & 0.91 & 0.59 & 0.74 & 0.37 & 0.80 \\ 
  \cline{2-12}
& \parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}} & Gamma & 0.62 & 0.76 & 0.42 & 0.99 & 0.71 & 0.86 & 0.10 & 0.89 \\ 
   &  &  & Lognormal & 0.50 & 0.47 & 0.95 & 1.00 & 0.64 & 0.84 & 0.09 & 0.97 \\ 
   &  &  & Weibull & 0.50 & 0.47 & 0.92 & 1.00 & 0.64 & 0.77 & 0.39 & 0.98 \\ 
  \cline{3-12}
 & & &   Exponential & 0.88 & 1.00 & 0.00 & 0.00 & 0.50 & 0.49 & 0.54 & 0.95 \\ 
  \cline{3-12}
 & & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} & Gamma & 0.24 & 0.01 & 0.00 & 0.00 & 0.52 & 0.53 & 0.76 & 0.99 \\ 
   &  &  & Lognormal & 0.18 & 0.00 & 0.00 & 0.00 & 0.49 & 0.47 & 0.66 & 0.97 \\ 
   &  &  & Weibull & 0.18 & 0.00 & 0.00 & 0.00 & 0.52 & 0.52 & 0.80 & 1.00 \\ 
   \hline
\end{tabular}
\caption{Summary of mixture vs. non-mixture model fits when the detection probability is $\pdet =0.50$.  
In all cases, the inference model family matches the dataset family.  
Med $p$: average across simulations of the posterior median of $\pdet$.  
Q($p$): average proportion of the posterior distribution of $\pdet$ that is larger than the true value.  
50\% and 90\% coverage is expressed as the proportion of 100 simulations for which the true value of $\pdet$ lies within the appropriate credible interval.}

@@

\begin{tabular}{l|l|l|l|cccc|cccc}
 \multicolumn{4}{c|}{ } & \multicolumn{4}{c|}{\underline{Non-mixture model}} & \multicolumn{4}{c}{\underline{Mixture model}} \\
 \multicolumn{4}{c|}{ } & Med $p$ & Q($p$) & 50\% & 90\% & Med $p$ & Q($p$) & 50\% & 90\% \\ 
  \hline
  \hline
 \parbox[t]{2mm}{\multirow{14}{*}{\rotatebox[origin=c]{90}{TTDD used to simulate data}}} & \parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Non-mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}}& Gamma & 0.69 & 0.59 & 0.78 & 0.98 & 0.78 & 0.79 & 0.35 & 0.90 \\ 
   &  &  & Lognormal & 0.59 & 0.31 & 0.45 & 0.91 & 0.73 & 0.69 & 0.63 & 0.90 \\ 
   &  &  & Weibull & 0.60 & 0.38 & 0.59 & 0.99 & 0.73 & 0.68 & 0.59 & 0.94 \\
  \cline{3-12}
   &  &  & Exponential & 0.64 & 0.47 & 0.50 & 0.85 & 0.61 & 0.29 & 0.33 & 0.82 \\ 
  \cline{3-12}
 & & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}}& Gamma & 0.64 & 0.44 & 0.46 & 0.89 & 0.68 & 0.66 & 0.51 & 0.85 \\ 
   &  &  & Lognormal & 0.64 & 0.47 & 0.36 & 0.87 & 0.67 & 0.63 & 0.44 & 0.79 \\ 
   &  &  & Weibull & 0.61 & 0.40 & 0.46 & 0.88 & 0.69 & 0.67 & 0.46 & 0.88 \\ 
  \cline{2-12}
& \parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}}& Gamma & 0.60 & 0.36 & 0.78 & 1.00 & 0.71 & 0.63 & 0.81 & 0.99 \\ 
   &  &  & Lognormal & 0.52 & 0.13 & 0.12 & 0.74 & 0.67 & 0.54 & 0.93 & 1.00 \\ 
   &  &  & Weibull & 0.51 & 0.17 & 0.23 & 0.82 & 0.66 & 0.52 & 0.92 & 1.00 \\ 
  \cline{3-12}
   &  &  & Exponential & 0.93 & 1.00 & 0.00 & 0.00 & 0.63 & 0.46 & 0.45 & 0.87 \\ 
  \cline{3-12}
 & & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} & Gamma & 0.26 & 0.00 & 0.00 & 0.00 & 0.58 & 0.34 & 0.51 & 0.95 \\ 
   &  &  & Lognormal & 0.20 & 0.00 & 0.00 & 0.00 & 0.61 & 0.41 & 0.58 & 0.92 \\ 
   &  &  & Weibull & 0.19 & 0.00 & 0.00 & 0.00 & 0.56 & 0.34 & 0.44 & 0.95 \\ 
   \hline
\end{tabular}
\caption{Summary of mixture vs. non-mixture model fits when the detection probability is $\pdet =0.65$.  
In all cases, the inference model family matches the dataset family.  
Med $p$: average across simulations of the posterior median of $\pdet$.  
Q($p$): average proportion of the posterior distribution of $\pdet$ that is larger than the true value.  
50\% and 90\% coverage is expressed as the proportion of 100 simulations for which the true value of $\pdet$ lies within the appropriate credible interval.}

\end{table}

\begin{table}[ht]\centering\footnotesize
\begin{tabular}{l|l|l|l|cccc|cccc}
 \multicolumn{4}{c|}{ } & \multicolumn{4}{c|}{\underline{Non-mixture model}} & \multicolumn{4}{c}{\underline{Mixture model}} \\
 \multicolumn{4}{c|}{ } & Med $p$ & Q($p$) & 50\% & 90\% & Med $p$ & Q($p$) & 50\% & 90\% \\ 
  \hline
  \hline
 \parbox[t]{2mm}{\multirow{14}{*}{\rotatebox[origin=c]{90}{TTDD used to simulate data}}} & \parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Non-mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}} & Gamma & 0.75 & 0.39 & 0.45 & 0.92 & 0.83 & 0.62 & 0.55 & 0.91 \\ 
   &  &  & Lognormal & 0.71 & 0.29 & 0.29 & 0.82 & 0.82 & 0.61 & 0.63 & 0.91 \\ 
   &  &  & Weibull & 0.72 & 0.34 & 0.41 & 0.86 & 0.82 & 0.60 & 0.59 & 0.93 \\ 
  \cline{3-12}
    &  &  & Exponential & 0.80 & 0.49 & 0.54 & 0.88 & 0.78 & 0.32 & 0.48 & 0.86 \\ 
  \cline{3-12}
 & & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} & Gamma & 0.79 & 0.44 & 0.45 & 0.87 & 0.81 & 0.59 & 0.45 & 0.90 \\ 
   &  &  & Lognormal & 0.80 & 0.48 & 0.52 & 0.95 & 0.81 & 0.60 & 0.53 & 0.92 \\ 
   &  &  & Weibull & 0.78 & 0.37 & 0.38 & 0.84 & 0.81 & 0.57 & 0.49 & 0.92 \\ 
  \cline{2-12}
& \parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}} & Gamma & 0.64 & 0.11 & 0.11 & 0.59 & 0.75 & 0.38 & 0.64 & 1.00 \\ 
   &  &  & Lognormal & 0.58 & 0.06 & 0.04 & 0.27 & 0.74 & 0.33 & 0.51 & 0.98 \\ 
   &  &  & Weibull & 0.54 & 0.04 & 0.01 & 0.23 & 0.70 & 0.27 & 0.46 & 1.00 \\ 
  \cline{3-12}
   &  &  & Exponential & 0.96 & 1.00 & 0.00 & 0.00 & 0.78 & 0.45 & 0.42 & 0.86 \\ 
  \cline{3-12}
 & & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} & Gamma & 0.28 & 0.00 & 0.00 & 0.00 & 0.72 & 0.30 & 0.40 & 0.80 \\ 
   &  &  & Lognormal & 0.22 & 0.00 & 0.00 & 0.00 & 0.78 & 0.45 & 0.46 & 0.87 \\ 
   &  &  & Weibull & 0.22 & 0.00 & 0.00 & 0.00 & 0.69 & 0.29 & 0.33 & 0.88 \\ 
   \hline
\end{tabular}
\caption{Summary of mixture vs. non-mixture model fits when the detection probability is $\pdet =0.80$.  
In all cases, the inference model family matches the dataset family.  
Med $p$: average across simulations of the posterior median of $\pdet$.  
Q($p$): average proportion of the posterior distribution of $\pdet$ that is larger than the true value.  
50\% and 90\% coverage is expressed as the proportion of 100 simulations for which the true value of $\pdet$ lies within the appropriate credible interval.}

>>>>

\documentclass[useAMS,usenatbib,referee,12pt]{article}
\usepackage[margin=1.0in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{parskip}
\usepackage[round]{natbib}
\usepackage{caption}
\usepackage{tabularx, booktabs}
\usepackage{float, placeins}
\usepackage{adjustbox}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{url}
\usepackage{xr}
\usepackage{listings}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{rotating}

\externaldocument[M-]{Draft}

@@

\section{Tables}
\begin{table}[!ht]
\centering
\begin{tabular}{lll|ccc}
  \hline
Family & Mixture & Peaked & $\gamma$ & $\varphi$ & $\alpha$ \\ 
  \hline
Exponential & Non-mixture & &  & -1.827 &  \\ 
  & Mixture & & 0.65 & -2.138 &  \\ 
  \hline
  Gamma & Non-mixture & Nonpeaked &  & -3.279 & 0.257 \\ 
  & & Peaked &  & -0.746 & 3.371 \\ 
  & Mixture & Nonpeaked & 0.65 & -2.773 & 0.577 \\ 
  & & Peaked & 0.65 & -1.210 & 2.491 \\ 
  \hline
  Lognormal & Non-mixture & Nonpeaked &  & -0.341 & 2.330 \\ 
  & & Peaked &  & -1.872 & 0.512 \\ 
  & Mixture & Nonpeaked & 0.65 & -1.462 & 1.674 \\ 
  & & Peaked & 0.65 & -1.992 & 0.618 \\ 
  \hline
  Weibull & Non-mixture & Nonpeaked &  & -1.165 & 0.418 \\ 
  & & Peaked &  & -2.042 & 1.829 \\ 
  & Mixture & Nonpeaked & 0.65 & -2.063 & 0.687 \\ 
  & & Peaked & 0.65 & -2.201 & 1.621 \\ 
   \hline
\end{tabular}
\caption{\label{simvals}Table of parameter values used to generate data for: (i) the mixture vs. non-mixture simulation, and (ii) the constant vs. non-constant rate simulation.  Here $\gamma$ is a mixing parameter for the proportion of `hard to detect' individuals, $\varphi$ is the detection rate parameter, and $\alpha$ is the shape parameter.}
\end{table}

@@

Gamma & Non-mixture & Nonpeaked &0.129&-0.001&0.098&-1.039&0.048&-0.104&-0.12&0.141&0.129 \\

@@

& Mixture & Nonpeaked &0.128&-0.005&0.079&-1.051&-0.048&-0.126&-0.042&0.21&0.2 \\

@@

Lognormal & Non-mixture & Nonpeaked &0.126&0.031&0.096&-1.047&0.163&-0.099&-0.071&0.31&0.079 \\

@@

& Mixture & Nonpeaked &0.126&0.017&0.07&-1.068&0.006&-0.14&-0.038&0.341&0.191 \\

@@

Weibull & Non-mixture & Nonpeaked &0.129&0.011&0.102&-1.04&0.101&-0.104&-0.127&0.204&0.086 \\

@@

& Mixture & Nonpeaked &0.129&-0.002&0.081&-1.049&-0.028&-0.122&-0.069&0.204&0.183 \\

@@

Gamma & Non-mixture & Nonpeaked &1.383&-3.941&0.121&0.072&0.39& & 0.316 \\

@@

& Mixture & Nonpeaked &1.215&-2.7&0.121&0.079&0.332&0.79& 0.597 \\

@@

Lognormal & Non-mixture & Nonpeaked &1.613&-2.444&0.151&0.077&0.353& & 3.287 \\

@@

& Mixture & Nonpeaked &1.282&-2.051&0.14&0.079&0.312&0.706& 1.467 \\

@@

Weibull & Non-mixture & Nonpeaked &1.57&-3.137&0.131&0.074&0.383& & 0.387 \\

@@

& Mixture & Nonpeaked &1.294&-2.354&0.122&0.078&0.344&0.814& 0.653 \\

@@

\caption{\label{tbl:sim3}Table of parameter values used to generate data for simulations with covariates (Section \ref{M-sec:simfull}).  Here, $\gamma$ is a mixing parameter for the proportion of `hard to detect' individuals, $\beta$'s are fixed effects, $\sigma$'s are random effect standard deviations, $\alpha$ is a shape parameter, and superscripts of $A$ and $D$ indicate abundance and detection parameters, respectively.}

@@

%  Gamma & Non-mixture & Nonpeaked & 1.383 & 0.129 & -0.001 & 0.098 & -1.039 & -3.941 & 0.048 & -0.104 & -0.120 & 0.141 & 0.129 & 0.121 & 0.072 & 0.390 &  & 0.316 \\ 

@@

%   & Mixture & Nonpeaked & 1.215 & 0.128 & -0.005 & 0.079 & -1.051 & -2.700 & -0.048 & -0.126 & -0.042 & 0.210 & 0.200 & 0.121 & 0.079 & 0.332 & 0.790 & 0.597 \\ 

@@

%  Lognormal & Non-mixture & Nonpeaked & 1.613 & 0.126 & 0.031 & 0.096 & -1.047 & -2.444 & 0.163 & -0.099 & -0.071 & 0.310 & 0.079 & 0.151 & 0.077 & 0.353 &  & 3.287 \\ 

@@

%   & Mixture & Nonpeaked & 1.282 & 0.126 & 0.017 & 0.070 & -1.068 & -2.051 & 0.006 & -0.140 & -0.038 & 0.341 & 0.191 & 0.140 & 0.079 & 0.312 & 0.706 & 1.467 \\ 

@@

%  Weibull & Non-mixture & Nonpeaked & 1.570 & 0.129 & 0.011 & 0.102 & -1.040 & -3.137 & 0.101 & -0.104 & -0.127 & 0.204 & 0.086 & 0.131 & 0.074 & 0.383 &  & 0.387 \\ 

@@

%   & Mixture & Nonpeaked & 1.294 & 0.129 & -0.002 & 0.081 & -1.049 & -2.354 & -0.028 & -0.122 & -0.069 & 0.204 & 0.183 & 0.122 & 0.078 & 0.344 & 0.814 & 0.653 \\ 

@@

\begin{table}[ht]
\footnotesize\centering
\begin{tabular}{l|l|l|l|cccc|cccc}
 \multicolumn{4}{c|}{ } & \multicolumn{4}{c|}{\underline{Non-mixture model}} & \multicolumn{4}{c}{\underline{Mixture model}} \\
 \multicolumn{4}{c|}{ } & Med $p$ & Q($p$) & 50\% & 90\% & Med $p$ & Q($p$) & 50\% & 90\% \\ 
  \hline
  \hline
 \parbox[t]{2mm}{\multirow{14}{*}{\rotatebox[origin=c]{90}{TTDD used to simulate data}}} & \parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Non-mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}} & Gamma & 0.67 & 0.84 & 0.11 & 0.94 & 0.76 & 0.92 & 0.00 & 0.70 \\ 
   &  &  & Lognormal & 0.54 & 0.60 & 0.81 & 1.00 & 0.68 & 0.88 & 0.05 & 0.79 \\ 
   &  &  & Weibull & 0.55 & 0.61 & 0.79 & 0.99 & 0.69 & 0.84 & 0.16 & 0.87 \\ 
  \cline{3-12}
 & & &  Exponential & 0.49 & 0.45 & 0.51 & 0.93 & 0.45 & 0.30 & 0.47 & 0.86 \\ 
  \cline{3-12}
 & & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} & Gamma & 0.48 & 0.46 & 0.57 & 0.90 & 0.57 & 0.72 & 0.42 & 0.85 \\ 
   &  &  & Lognormal & 0.49 & 0.45 & 0.53 & 0.93 & 0.54 & 0.69 & 0.37 & 0.89 \\ 
   &  &  & Weibull & 0.48 & 0.48 & 0.40 & 0.91 & 0.59 & 0.74 & 0.37 & 0.80 \\ 
  \cline{2-12}
& \parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}} & Gamma & 0.62 & 0.76 & 0.42 & 0.99 & 0.71 & 0.86 & 0.10 & 0.89 \\ 
   &  &  & Lognormal & 0.50 & 0.47 & 0.95 & 1.00 & 0.64 & 0.84 & 0.09 & 0.97 \\ 
   &  &  & Weibull & 0.50 & 0.47 & 0.92 & 1.00 & 0.64 & 0.77 & 0.39 & 0.98 \\ 
  \cline{3-12}
 & & &   Exponential & 0.88 & 1.00 & 0.00 & 0.00 & 0.50 & 0.49 & 0.54 & 0.95 \\ 
  \cline{3-12}
 & & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} & Gamma & 0.24 & 0.01 & 0.00 & 0.00 & 0.52 & 0.53 & 0.76 & 0.99 \\ 
   &  &  & Lognormal & 0.18 & 0.00 & 0.00 & 0.00 & 0.49 & 0.47 & 0.66 & 0.97 \\ 
   &  &  & Weibull & 0.18 & 0.00 & 0.00 & 0.00 & 0.52 & 0.52 & 0.80 & 1.00 \\ 
   \hline
\end{tabular}
\caption{Summary of mixture vs. non-mixture model fits when the detection probability is $\pdet =0.50$.  
In all cases, the inference model family matches the dataset family.  
Med $p$: average across simulations of the posterior median of $\pdet$.  
Q($p$): average proportion of the posterior distribution of $\pdet$ that is larger than the true value.  
50\% and 90\% coverage is expressed as the proportion of 100 simulations for which the true value of $\pdet$ lies within the appropriate credible interval.}
\label{tbl:mix50}

@@

\begin{tabular}{l|l|l|l|cccc|cccc}
 \multicolumn{4}{c|}{ } & \multicolumn{4}{c|}{\underline{Non-mixture model}} & \multicolumn{4}{c}{\underline{Mixture model}} \\
 \multicolumn{4}{c|}{ } & Med $p$ & Q($p$) & 50\% & 90\% & Med $p$ & Q($p$) & 50\% & 90\% \\ 
  \hline
  \hline
 \parbox[t]{2mm}{\multirow{14}{*}{\rotatebox[origin=c]{90}{TTDD used to simulate data}}} & \parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Non-mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}}& Gamma & 0.69 & 0.59 & 0.78 & 0.98 & 0.78 & 0.79 & 0.35 & 0.90 \\ 
   &  &  & Lognormal & 0.59 & 0.31 & 0.45 & 0.91 & 0.73 & 0.69 & 0.63 & 0.90 \\ 
   &  &  & Weibull & 0.60 & 0.38 & 0.59 & 0.99 & 0.73 & 0.68 & 0.59 & 0.94 \\
  \cline{3-12}
   &  &  & Exponential & 0.64 & 0.47 & 0.50 & 0.85 & 0.61 & 0.29 & 0.33 & 0.82 \\ 
  \cline{3-12}
 & & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}}& Gamma & 0.64 & 0.44 & 0.46 & 0.89 & 0.68 & 0.66 & 0.51 & 0.85 \\ 
   &  &  & Lognormal & 0.64 & 0.47 & 0.36 & 0.87 & 0.67 & 0.63 & 0.44 & 0.79 \\ 
   &  &  & Weibull & 0.61 & 0.40 & 0.46 & 0.88 & 0.69 & 0.67 & 0.46 & 0.88 \\ 
  \cline{2-12}
& \parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}}& Gamma & 0.60 & 0.36 & 0.78 & 1.00 & 0.71 & 0.63 & 0.81 & 0.99 \\ 
   &  &  & Lognormal & 0.52 & 0.13 & 0.12 & 0.74 & 0.67 & 0.54 & 0.93 & 1.00 \\ 
   &  &  & Weibull & 0.51 & 0.17 & 0.23 & 0.82 & 0.66 & 0.52 & 0.92 & 1.00 \\ 
  \cline{3-12}
   &  &  & Exponential & 0.93 & 1.00 & 0.00 & 0.00 & 0.63 & 0.46 & 0.45 & 0.87 \\ 
  \cline{3-12}
 & & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} & Gamma & 0.26 & 0.00 & 0.00 & 0.00 & 0.58 & 0.34 & 0.51 & 0.95 \\ 
   &  &  & Lognormal & 0.20 & 0.00 & 0.00 & 0.00 & 0.61 & 0.41 & 0.58 & 0.92 \\ 
   &  &  & Weibull & 0.19 & 0.00 & 0.00 & 0.00 & 0.56 & 0.34 & 0.44 & 0.95 \\ 
   \hline
\end{tabular}
\caption{Summary of mixture vs. non-mixture model fits when the detection probability is $\pdet =0.65$.  
In all cases, the inference model family matches the dataset family.  
Med $p$: average across simulations of the posterior median of $\pdet$.  
Q($p$): average proportion of the posterior distribution of $\pdet$ that is larger than the true value.  
50\% and 90\% coverage is expressed as the proportion of 100 simulations for which the true value of $\pdet$ lies within the appropriate credible interval.}
\label{tbl:mix65}
\end{table}

\begin{table}[ht]\centering\footnotesize
\begin{tabular}{l|l|l|l|cccc|cccc}
 \multicolumn{4}{c|}{ } & \multicolumn{4}{c|}{\underline{Non-mixture model}} & \multicolumn{4}{c}{\underline{Mixture model}} \\
 \multicolumn{4}{c|}{ } & Med $p$ & Q($p$) & 50\% & 90\% & Med $p$ & Q($p$) & 50\% & 90\% \\ 
  \hline
  \hline
 \parbox[t]{2mm}{\multirow{14}{*}{\rotatebox[origin=c]{90}{TTDD used to simulate data}}} & \parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Non-mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}} & Gamma & 0.75 & 0.39 & 0.45 & 0.92 & 0.83 & 0.62 & 0.55 & 0.91 \\ 
   &  &  & Lognormal & 0.71 & 0.29 & 0.29 & 0.82 & 0.82 & 0.61 & 0.63 & 0.91 \\ 
   &  &  & Weibull & 0.72 & 0.34 & 0.41 & 0.86 & 0.82 & 0.60 & 0.59 & 0.93 \\ 
  \cline{3-12}
    &  &  & Exponential & 0.80 & 0.49 & 0.54 & 0.88 & 0.78 & 0.32 & 0.48 & 0.86 \\ 
  \cline{3-12}
 & & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} & Gamma & 0.79 & 0.44 & 0.45 & 0.87 & 0.81 & 0.59 & 0.45 & 0.90 \\ 
   &  &  & Lognormal & 0.80 & 0.48 & 0.52 & 0.95 & 0.81 & 0.60 & 0.53 & 0.92 \\ 
   &  &  & Weibull & 0.78 & 0.37 & 0.38 & 0.84 & 0.81 & 0.57 & 0.49 & 0.92 \\ 
  \cline{2-12}
& \parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}} & Gamma & 0.64 & 0.11 & 0.11 & 0.59 & 0.75 & 0.38 & 0.64 & 1.00 \\ 
   &  &  & Lognormal & 0.58 & 0.06 & 0.04 & 0.27 & 0.74 & 0.33 & 0.51 & 0.98 \\ 
   &  &  & Weibull & 0.54 & 0.04 & 0.01 & 0.23 & 0.70 & 0.27 & 0.46 & 1.00 \\ 
  \cline{3-12}
   &  &  & Exponential & 0.96 & 1.00 & 0.00 & 0.00 & 0.78 & 0.45 & 0.42 & 0.86 \\ 
  \cline{3-12}
 & & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} & Gamma & 0.28 & 0.00 & 0.00 & 0.00 & 0.72 & 0.30 & 0.40 & 0.80 \\ 
   &  &  & Lognormal & 0.22 & 0.00 & 0.00 & 0.00 & 0.78 & 0.45 & 0.46 & 0.87 \\ 
   &  &  & Weibull & 0.22 & 0.00 & 0.00 & 0.00 & 0.69 & 0.29 & 0.33 & 0.88 \\ 
   \hline
\end{tabular}
\caption{Summary of mixture vs. non-mixture model fits when the detection probability is $\pdet =0.80$.  
In all cases, the inference model family matches the dataset family.  
Med $p$: average across simulations of the posterior median of $\pdet$.  
Q($p$): average proportion of the posterior distribution of $\pdet$ that is larger than the true value.  
50\% and 90\% coverage is expressed as the proportion of 100 simulations for which the true value of $\pdet$ lies within the appropriate credible interval.}
\label{tbl:mix80}
